KIN: A method to infer relatedness from low-coverage ancient DNA

### 2022-05-16 paper_overleaf/KIN_a_method_to_estimate_relatedness_from_low_coverage_data_supplements.tex

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/egplot2.png}
    \caption{Plots showing proportion of differences in windows along the genome for some of the pairs of relatives for which KIN differs from lcMLkin. (A) AITI43-AITI55 (READ estimates First degree, lcMLkin predicts siblings, while KIN predicts parent-child. (B) AITI70-AITI72 (READ estimates First degree, lcMLkin predicts parent-child, while KIN predicts siblings.}
    \label{figS9:eg2}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/egplot2.png}
    \caption{Plots showing proportion of differences in windows along the genome for the first degree relatives for which KIN differs from lcMLkin. We expect to see proportion of difference to be close to $p_0$ in $25\%$ windows, $p_1$ in $50\%$ windows, and $p_2$ in $25\%$ windows. For parent-child, we expect the proportion of differences to stay close to $p_1$ with some noise. (A) AITI43-AITI55 (READ estimates first degree, lcMLkin predicts siblings, while KIN predicts parent-child. (B) AITI70-AITI72 (READ estimates first degree, lcMLkin predicts parent-child, while KIN predicts siblings. (C) OBKR76-POST99 (READ estimates first degree, lcMLkin predicts siblings, while KIN predicts parent-child.}
    \label{figS9:eg2}
\end{figure}
